This is an example of article title

### 2023-07-02 paper/paper.tex
chore: Thread scaling additions to paper

@@

\section{Experiments}
\subsection{Dimensionality scaling}
For $n=10^5$ uniformly distributed points we computed the average number of points in a
leaf node of the tree. The graph \ref{b_vs_d} shows that for increasingly higher
dimensional spaces the data get exponatialy sparser.

@@

>>>>

Our implementation utilizes a watefall scheme to adapt to the needs of the problem at
hand. There are $3$ different thresholds that can tune the runtime performance of the
spatial partitioning.

\begin{itemize}
  \item \verb|Huge| threshold
  \item \verb|Big| threshold
  \item \verb|Small| threshold
\end{itemize}

$$ \textrm{Huge} > \textrm{Big} > \textrm{Small} $$

For sub-arrays that are larger than the \verb|Huge| threshold our implementation
uses parallel \verb|MSD Radixsort|, otherwise it falls back to the non parallel variant.
\\\\
For sub-arrays that are larger than the \verb|Big| threshold our implementation uses
parallel \verb|Countsort|, otherwise it falls back to the non parallel variant.
\\\\
For sub-arrays that are smaller than the \verb|Small| threshold our implementation
stops the recursion of \verb|MSD Radixsort|.

@@

\section{Experiments}
All conducted experiments are executed with a selected radix of $16$ bits and the array
is fully sorted.

\subsection{Dimensionality scaling}
For $n=10^5$ uniformly distributed points we computed the average number of points in a
leaf node of the tree. The graph \ref{b_vs_d} shows that for increasingly higher
dimensional spaces the data get exponatialy sparser.

@@

\subsection{Runtime performance}
\subsubsection{Scaling with number of points}
For $l=4$ max tree depth and $d=4$ number of dimensions
\verb|AdaptiveHierarchicalRegularBinning.jl| scales linearly with the size of the array
$n$.

\begin{figure}[!ht]
  \centerline{
    \includegraphics[width=20pc]{figures/experiments/scale_n.png}
  }
  \caption{ Linear runtime scaling }
  \label{scale_n}
\end{figure}

\subsubsection{Runtime dimensionality scaling}
High dimensionality should affect the morton encoding since bit-interleaving scales
linearly with the dimensions. The reordering should be affected slightly since each
element

% TODO

\subsubsection{Scaling with number of threads}
For $n=10^6$ points of $d=10$ dimensions and a target tree of $l=4$
levels, we can see from \ref{scale_t} that the scaling of
\verb|AdaptiveHierarchicalRegularBinning.jl| drops exponatialy
with the number of threads.

\begin{figure}[!ht]
  \centerline{
    \includegraphics[width=20pc]{figures/experiments/scale_t.png}
  }
  \caption{ Parallelization scaling }
  \label{scale_t}
\end{figure}
